A Practical Optional Type System for Clojure

### 2012-10-27 dissertation/intro.tex
Fix wording on hmaps, suggested by nDuff

Clojure emphasises key-value paired, unordered \emph{maps} for many uses where other languages might use objects
Clojure provides a map literal using curly braces. For example,
\lstinline|{:a 1, :b 2}| is a map value with two key-value entries: from keyword key \lstinline|:a|
to value \lstinline|1|, and keyword key \lstinline|:b| to value \lstinline|2|. Note that commas are always
whitespace in Clojure and are included occasionally for readability.

>>>>

It is idiomatic in Clojure to use plain maps with known keyword keys as lightweight objects.
Clojure provides a hash-map literal (using curly braces), making this idiom particularly
convenient.
For example,
\lstinline|{:a 1, :b 2}| is a map value with two key-value entries: from keyword key \lstinline|:a|
to value \lstinline|1|, and keyword key \lstinline|:b| to value \lstinline|2|. Note that commas are always
whitespace in Clojure and are included occasionally for readability.
